\speculake: Hiding Malware in Speculative Execution

### 2018-05-09 paper/figures.tex
edit fig cap

    \caption{The number of instructions and success rate of a the 5-state Busy 
    Beaver configuration were measured as a function of how many iterations 
    into the speculative world were performed. We see that the amount of time 
    to reach 20,000 instructions completed is a linear function of how many 
    indirect calls into the speculative world we take. Additionally we see that 
    it only requires using 4 speculative calls to achieve no errors in reaching 
    20,000 instructions.}

>>>>

    \caption{The number of instructions and error rate of a the 5-state Busy
            Beaver configuration were measured as a function of how many (redundant) iterations into
    the speculative world were performed. As expected, the amount of time to
    complete a million instructions is a linear function of how many
    indirect calls into the speculative world we take. Additionally we see that
    it only requires using 10 speculative calls per instruction to achieve a
    very low number of errors in reaching a million instructions, making 10-20
    iterations an attractive choice for most applications.}
